Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-04 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:04	20:58:58	(Sun 4.Oct)

This article is outlined as follows: In Section \ref{sec:beamforming} we introduce beamforming, followed by background on the MVDR beamformer in Section \ref{sec:mvdr}. In \ref{sec:lca} we provide complete background on the LCA method, by presenting the Kaiser window function in \ref{sec:lca_kaiser_windows}, the method for steering it in \ref{sec:lca_steering} as well as a note on maximum steering amount in \ref{sec:lca_steering_bounds}, and a mention of the alternative trigonometric window function in \ref{sec:lca_trigonometric} and sampling considerations in \ref{sec:lca_oversampling}. Results and discussion is provided in Section \ref{sec:results_discussion}, where we study MVDR to find suitable LCA windows in \ref{sec:results_lca_window_function}, assess how big the range of window types and steering should be in \ref{sec:results_window_parameters}, study image quality to determine the number of windows needed in \ref{sec:results_database_size}, and

>>>>

This article is outlined as follows: In Section \ref{sec:beamforming} we offer a gentle introduction to beamforming. Then we move on to adaptive beamforming and describe the MVDR and LCA methods \ref{sec:mvdr} and \ref{sec:lca}, respectively. We use LCA with the Kaiser window which we describe in \ref{sec:lca_kaiser_windows}, and explain how we steer it in \ref{sec:lca_steering}, and by how much in \ref{sec:lca_steering_bounds}. Finally we add some remarks on using the trigonometric window instead of Kaiser in \ref{sec:lca_trigonometric}, and of of sampling considerations in \ref{sec:lca_oversampling}. Results and discussion is provided in Section \ref{sec:results_discussion}, where we study MVDR to find suitable LCA windows in \ref{sec:results_lca_window_function}, assess how big the range of window types and steering should be in \ref{sec:results_window_parameters}, study image quality to determine the number of windows needed in \ref{sec:results_database_size}, and
